### 2020-09-29 paper/natastron/paper.tex
Finished main body

\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases. We found that the joint posterior distribution did not change significantly when excluding stars with a metallicity outside the model range (purple in Figure \ref{fig:fullsample}), or those with extremely small uncertainties on asteroseismic mass.Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.

The same was true when repeating the analysis with increased uncertainties on asteroseismic mass and age, or when shifting asteroseismic ages younger by their systematic uncertainties \cite{silvaaguirre+2015, silvaaguirre+2017}.  For a full discussion of these tests and other biases, see \textbf{\textit{Methods}}.\\

Section 5.2.5.

@@

	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors.

	\item The new asteroseismic rotation catalogue presented in this work will act as an entry point for more detailed studies, including comparisons between different braking laws and individually modeled values of stellar rotation at different critical Rossby numbers.
\end{enumerate}

Finally, in the near future our asteroseismic rotation catalogue will be further complemented; with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}; and new asteroseismic measurements of age from the \ktwo and \tess missions. With these surveys, large scale ensemble asteroseismology will continue to increase the possibilities for understanding gyrochronology.\\

@@

\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\

@@

\textbf{Author Contributions:} O.J.H. led the project, with help from G.R.D., J.V.S., M.B.N and W.J.C.. J.V.S. also led the development of the stellar population models. M.N.L., R.A.G. and S.K. both provided data or stellar models and along with J.T. assessed the validity of our asteroseismic results. L.A., A.B. and V.S. provided the assessment of the theoretical implications of the gyrochronology results. All authors have contributed to the interpretation of the data and the results, and all discussed and provided comments for all drafts of the paper.

>>>>

\textbf{Verifying consequences for gyrochronology:} In order to verify that our results presented a meaningful confirmation of weakened magnetic braking, we ensured that the same results were obtained when using different subsets of the ensemble, and when exploring potential biases. We found that the joint posterior distribution did not change significantly when excluding stars with a metallicity outside the model range (purple in Figure \ref{fig:fullsample}), or those with extremely small uncertainties on asteroseismic mass. Stars in our sample with known binary companions that may disrupt their rotational evolution were not found to contribute strongly to the joint posterior probability of $P_{\rm s}$.

We checked that our results remained the same if the `Kages' and LEGACY catalogues had underestimated the uncertainties on the asteroseismic mass and age, which form part of our mixture model analysis. We reran our analysis after inflating the uncertainties on these properties to align with the expected systematic uncertainty from stellar models \cite{silvaaguirre+2015,silvaaguirre+2017}. The results from this echoed what we found for the unaltered ensemble. We also accounted for the possibility that asteroseismic methods systematically overestimated stellar age, and reran our analysis after shifting the seismic ages younger by their systematic uncertainty. This resulted in $95.8\%$ of the posterior probability to lie below $P_{\rm s} = 0.5$, compared to $98.4\%$ for the unaltered ensemble. From this, we can infer that our conclusions are robust against (relatively severe) potential issues in seismic analyses. For a full discussion of these tests and other biases, see \textbf{\textit{Methods}}.\\

Weakened magnetic braking was first proposed by van Saders et al. (2016) \cite[hereafter the `van Saders' study]{vansaders+2016} in response to stars with spot rotation rates faster than expected from gyrochronology at their asteroseismic ages \cite{vansaders+2016}. This discrepancy was also indicated at around the same time in other studies of asteroseismic ages of main sequence stars \cite{nielsen+2015, angus+2015, davies+2015}. The theory of weakened magnetic braking has been both reinforced by recent studies \cite{metcalfe+egeland2019}, as well as disputed \cite{lorenzo-oliveira+2019}, at least at the critical Rossby number originally proposed.

A recent study using spectroscopic rotation measurements of 14 solar twins, compared to grids of stellar models, found marginal evidence favouring a standard rotational evolution \cite{lorenzo-oliveira+2019}. If weakened magnetic braking were to take place, this work proposed that it would most likely be outside the range of their sample, at $Ro_{\rm {crit}} \geq 2.29$, compared to the value of $1.97$ used in this work. Our sample does not overlap with theirs, so we can not directly compare to their results. However, our work does find statistical agreement between our asteroseismic rotation rates and ages, and a model of weakened magnetic braking at a critical Rossby number of $1.97$. A comparison to models of different Rossby numbers will be explored in future papers, using the LEGACY and Kages rotation sample presented in this work.

As a sanity check that the evidence in favour of weakened magnetic braking presented in this work is independently robust, we recreated the joint posterior probability for $P_{\rm s}$, this time looking only at MS stars, and excluding any of the 22 stars that were included in the original van Saders study used to detect weakened magnetic braking. Of the 47 MS stars used to distinguish between stellar models, 16 were included in the van Saders sample. Both the 16 stars in the original van Saders study as well as the remaining MS stars favoured the WMB model, although the van Saders stars did so more strongly, not including any stars that favoured the standard model. Specifically, when considering only the van Saders stars, $96.3\%$ of the total joint probability lay below $P_{\rm s} = 0.5$, compared to $91.7\%$ when considering only those stars \emph{not} included in the van Saders study. The stars initially used to propose the WMB model are still those most strongly in favour of it even when using asteroseismic rotation rates only, a result which is now further reinforced by an expanded sample that includes quiescent stars.\\

\textbf{Conclusions:} In this work, we obtained asteroseismic rotation rates for 91 stars using a hierarchical Bayesian model to fit for oscillation frequencies, convective background, and rotational splitting simultaneously. We validated these results against previously published and unpublished asteroseismic rotation measurements, making our new rotation catalogue the largest self-consistent sample of asteroseismic rotation in main sequence stars to date. We evaluated the stars in our sample against synthetic population models of the \textit{Kepler} field evolved under either a `standard' model of rotational evolution, or one where weakened magnetic braking takes place. This evaluation was done using a Bayesian mixture model to determine whether the ensemble preferred one model over another, and was done in simultaneously in asteroseismic rotation, mass, age, and spectroscopic temperature and metallicity.\\

@@

	\item We present new techniques for asteroseismic `peak-bagging' frequency analyses, specifically: expressing well known empirical asteroseismic relations in a hierarchical modeling structure to account for small-scale effects not included in our model (such as acoustic glitches), and replacing uninformative empirical relations with Gaussian Process priors, detailed in the \textit{\textbf{Supplementary Information}}.

\end{enumerate}

In the near future this asteroseismic rotation catalogue will be further complemented with high-precision surface rotation measurements and atmospheric parameters from spectroscopic surveys such as LAMOST \cite{deng+2012}, 4MOST \cite{dejong+2014} and WEAVE \cite{dalton+2014}, and new asteroseismic measurements of age from the \ktwo and \tess missions. With these surveys, large scale ensemble asteroseismology will continue to increase the possibilities for understanding gyrochronology.\\

@@

%\textbf{Software}: \texttt{astropy} \cite{astropycollaboration+2013, astropycollaboration+2018}, \texttt{astroquery} \cite{ginsburg+2019}, \texttt{Lightkurve} \cite{lightkurvecollaboration+2018}, \texttt{corner} \cite{foreman-mackey2016}, \texttt{emcee} \cite{foreman-mackey+2013}, \href{https://docs.daft-pgm.org/}{\texttt{daft}}, \texttt{Stan} \cite{carpenter+2017}, \texttt{PyStan} \cite{vanhoey+2013}, \texttt{iPython} \cite{perez+granger2007}, \texttt{Jupyter Notebooks} \cite{kluyver+2016}, \texttt{numpy}  \cite{vanderwalt+2011}, \texttt{pandas} and \texttt{scipy} \cite{mckinney2010}, \texttt{matplotlib} \cite{hunter2007}, \texttt{seaborn} \cite{waskom+2018}, \texttt{statsmodels} \cite{seabold+perktold2010}, \texttt{PyMC3} \cite{salvatier+2016}, \texttt{theano} \cite{thetheanodevelopmentteam+2016}.\\

@@

\textbf{Author Contributions:} O.J.H. led the project, with help from G.R.D., J.V.S., M.B.N and W.J.C.. J.V.S. also led the development of the stellar population models. M.N.L., R.A.G. and S.K. provided data or stellar models and along with J.T. assessed the validity of our asteroseismic results. L.A., A.B. and V.S. provided the assessment of the theoretical implications of the gyrochronology results. All authors have contributed to the interpretation of the data and the results, and all discussed and provided comments for all drafts of the paper.
